### 2015-06-11 ApresentacoesArtigos/quali/quali.tex
adiantos na intro

Next subsections present a
% 1/N^2 == physics of humans, they are the agents
% Interacting with own network, with constant feedback, study of the self
% Annotation of own data, study of them. Extend analysis within the route.
%In this work, we present advances in handing the participant ways to explore and harness the social networks he/she participates in.
%This is not an easy task, therefore we selected

@@

\section{Anthropological physics}
The study of human systems raises conceptual
and ethical issues that require anthropological considerations.
There are two immediate routes to this concepts:
\begin{itemize}
	\item What data should or can be used?
	\item Can one experiment in a network of humans? In which context?
\end{itemize}

@@

\subsubsection{Gradus}
Fazer o $2^(100 2)$

>>>>

Next section presents directions on related work. Section~\ref{sec:mat} is dedicated to the data analyzed. Section~\ref{sec:met} holds the methods used to reach results. Results are given in Section~\ref{sec:res}. The chronogram and outline of finished, ongoing and planed tasks are in Section~\ref{sec:chr}. Conclusions are in Section~\ref{sec:con} followed by acknowledgments and the bibliography.
% Interacting with own network, with constant feedback, study of the self
% Annotation of own data, study of them. Extend analysis within the route.
%In this work, we present advances in handing the participant ways to explore and harness the social networks he/she participates in.
%This is not an easy task, therefore we selected

@@

\subsubsection{Anthropological physics}
The study of human systems raises conceptual
and ethical issues that require anthropological considerations.
There are two immediate routes to this concepts:
\begin{itemize}
	\item What data should or can be used?
	\item Can one experiment in a network of humans? In which context?
\end{itemize}

@@

\subsubsection{Gradus}
% 1/N^2 == physics of humans, they are the agents
Fazer o $2^(100 2)$
